---
title: "Multiple Treatment Groups Impact Evaluation: Advanced Methods for Employment Policy Analysis"
author: "longworkR Package"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Multiple Treatment Groups Impact Evaluation: Advanced Methods for Employment Policy Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 7,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)

# Load required libraries
library(longworkR)
library(data.table)
library(ggplot2)
library(dplyr)
library(tidyr)
library(viridis)
library(RColorBrewer)
```

# Introduction

## The Challenge of Multiple Treatment Groups

Employment policy evaluation frequently involves complex treatment scenarios where individuals may receive different types or intensities of interventions. Traditional impact evaluation methods designed for binary treatment scenarios (treatment vs. control) may be insufficient for understanding:

- **Multiple Program Types**: Job training vs. wage subsidies vs. placement assistance
- **Treatment Intensity**: Full-time vs. part-time training programs
- **Sequential Treatments**: Individuals receiving multiple interventions over time
- **Bundled Interventions**: Programs combining multiple components (training + subsidies + counseling)
- **Dose-Response Relationships**: How outcomes vary with treatment intensity or duration

This vignette demonstrates advanced methods for evaluating multiple treatment scenarios using the `longworkR` package, focusing on practical implementation with real-world employment data.

## Methodological Framework

### Core Challenges in Multiple Treatment Evaluation

1. **Selection Bias Across Treatment Groups**: Different types of individuals may select into (or be selected for) different treatment types
2. **Confounding by Treatment Intensity**: Individuals receiving more intensive treatments may have different baseline characteristics
3. **Multiple Comparison Problems**: Testing multiple treatment effects increases the risk of false discoveries
4. **Heterogeneous Treatment Effects**: Effects may vary across subgroups and treatment combinations
5. **Dynamic Treatment Assignment**: Treatments may be assigned based on previous outcomes or characteristics

### Methodological Approaches Covered

This vignette covers several methodological approaches:

- **Generalized Difference-in-Differences**: Extending DiD to multiple treatment groups and time periods
- **Propensity Score Matching with Multiple Treatments**: Using generalized propensity scores
- **Dose-Response Analysis**: Examining continuous treatment intensity
- **Machine Learning Methods**: Random forests and causal forests for heterogeneous effects
- **Synthetic Control Extensions**: Multiple donor pools and treatment timing
- **Treatment Effect Heterogeneity Analysis**: Exploring how effects vary across subgroups

# Data Preparation and Setup

## Sample Data Generation

Let's begin by creating a comprehensive synthetic dataset that mirrors real-world employment policy scenarios:

```{r data-setup}
# Set seed for reproducibility
set.seed(42)

# Generate comprehensive employment data with multiple treatments
generate_multi_treatment_data <- function(n_individuals = 2000, 
                                        n_time_periods = 8,
                                        treatment_start_period = 4) {
  
  cat("Generating multi-treatment employment data...\n")
  cat("Individuals:", n_individuals, "\n")
  cat("Time periods:", n_time_periods, "\n")
  cat("Treatment start:", treatment_start_period, "\n\n")
  
  # Individual-level characteristics (time-invariant)
  individuals <- data.table(
    cf = 1:n_individuals,
    # Demographics
    age = round(runif(n_individuals, 22, 55)),
    gender = sample(c("M", "F"), n_individuals, replace = TRUE),
    education = sample(c("basic", "secondary", "tertiary"), n_individuals, 
                      replace = TRUE, prob = c(0.3, 0.5, 0.2)),
    region = sample(c("north", "center", "south", "islands"), n_individuals, 
                   replace = TRUE, prob = c(0.3, 0.25, 0.35, 0.1)),
    
    # Baseline employment characteristics
    baseline_employment_rate = pmax(0, pmin(1, rnorm(n_individuals, 0.6, 0.3))),
    baseline_wage = pmax(800, rnorm(n_individuals, 2200, 600)),
    previous_unemployment_duration = pmax(0, rexp(n_individuals, 1/180)), # days
    sector_experience = sample(c("manufacturing", "services", "construction", "other"), 
                              n_individuals, replace = TRUE, prob = c(0.25, 0.45, 0.15, 0.15)),
    
    # Unobserved heterogeneity (affects both selection and outcomes)
    motivation = rnorm(n_individuals, 0, 1),
    ability = rnorm(n_individuals, 0, 1),
    
    # Network effects and regional characteristics
    regional_unemployment = rnorm(n_individuals, 0.08, 0.02),
    network_quality = rnorm(n_individuals, 0, 1)
  )
  
  # Treatment assignment mechanism (realistic selection process)
  # Probability of treatment depends on individual characteristics
  individuals[, prob_any_treatment := plogis(
    -1.2 + 
    0.3 * (age - mean(age)) / sd(age) +  # Older individuals more likely
    0.4 * (education == "basic") +        # Lower education more likely
    0.5 * (baseline_employment_rate < 0.4) + # Unemployed more likely
    0.3 * (previous_unemployment_duration > 365) + # Long-term unemployed
    -0.2 * ability +                      # Lower ability more likely
    0.1 * motivation +                    # More motivated more likely
    0.2 * (regional_unemployment > 0.08)  # High unemployment regions
  )]
  
  # Assign treatments (mutually exclusive for simplicity)
  individuals[, treatment_type := "control"]
  
  # Sample treatment recipients
  treatment_eligible <- which(runif(n_individuals) < individuals$prob_any_treatment)
  
  # Among eligible, assign specific treatment types
  treatment_types <- c("job_training", "wage_subsidy", "placement_assistance", "comprehensive")
  
  for (i in treatment_eligible) {
    # Conditional probabilities for different treatment types
    probs <- c(
      0.3,  # job_training
      0.25 + 0.2 * (individuals$baseline_wage[i] < 1800), # wage_subsidy (more likely for low-wage)
      0.25 + 0.15 * (individuals$sector_experience[i] == "services"), # placement_assistance
      0.2 + 0.1 * (individuals$education[i] == "basic")   # comprehensive (more likely for low-educated)
    )
    probs <- probs / sum(probs)
    individuals$treatment_type[i] <- sample(treatment_types, 1, prob = probs)
  }
  
  # Treatment intensity (for dose-response analysis)
  individuals[treatment_type != "control", treatment_intensity := runif(.N, 0.3, 1.0)]
  individuals[treatment_type == "control", treatment_intensity := 0]
  
  # Treatment duration (realistic variation)
  individuals[treatment_type == "job_training", treatment_duration := 
              pmax(30, rnorm(.N, 180, 60))]  # 3-9 months
  individuals[treatment_type == "wage_subsidy", treatment_duration := 
              pmax(60, rnorm(.N, 365, 90))]  # 6-15 months
  individuals[treatment_type == "placement_assistance", treatment_duration := 
              pmax(14, rnorm(.N, 90, 30))]   # 2-4 months
  individuals[treatment_type == "comprehensive", treatment_duration := 
              pmax(90, rnorm(.N, 270, 90))]  # 6-12 months
  individuals[treatment_type == "control", treatment_duration := 0]
  
  cat("Treatment assignment summary:\n")
  print(table(individuals$treatment_type))
  cat("\nTreatment intensity by type:\n")
  print(individuals[treatment_type != "control", 
                   .(mean_intensity = mean(treatment_intensity),
                     mean_duration = mean(treatment_duration)), 
                   by = treatment_type])
  
  # Generate time-varying outcomes
  panel_data <- data.table()
  
  for (period in 1:n_time_periods) {
    
    # Time period indicators
    is_pre_treatment <- period < treatment_start_period
    is_treatment_period <- period >= treatment_start_period
    periods_since_treatment <- pmax(0, period - treatment_start_period)
    
    period_data <- copy(individuals)
    period_data[, period := period]
    period_data[, post_treatment := as.numeric(is_treatment_period)]
    period_data[, periods_since_treatment := periods_since_treatment]
    
    # Generate employment outcomes with realistic dynamics
    
    # Base employment rate (with individual fixed effects and time trends)
    period_data[, base_employment := plogis(
      # Individual fixed effects
      -0.5 + 
      0.3 * (age - mean(age)) / sd(age) +
      0.2 * (education == "tertiary") - 0.1 * (education == "basic") +
      0.1 * ability +
      0.05 * motivation +
      
      # Time trends and regional effects  
      0.02 * period +  # General time trend
      -regional_unemployment * 2 +
      
      # Lagged employment (persistence)
      0.6 * baseline_employment_rate +
      
      # Random variation
      rnorm(.N, 0, 0.3)
    )]
    
    # Treatment effects (realistic timing and decay)
    # Job training: builds up over time, permanent gains
    period_data[treatment_type == "job_training" & is_treatment_period, 
                employment_effect := (
                  0.15 * treatment_intensity *  # Max effect 15pp
                  pmin(1, periods_since_treatment / 3) *  # Builds up over 3 periods
                  (1 + 0.1 * ability)  # Heterogeneous by ability
                )]
    
    # Wage subsidy: immediate effect, decays after treatment ends
    period_data[treatment_type == "wage_subsidy" & is_treatment_period, 
                employment_effect := (
                  0.20 * treatment_intensity *  # Max effect 20pp
                  exp(-0.1 * pmax(0, periods_since_treatment - treatment_duration/30))  # Decay after treatment
                )]
    
    # Placement assistance: quick effect, moderate persistence
    period_data[treatment_type == "placement_assistance" & is_treatment_period, 
                employment_effect := (
                  0.12 * treatment_intensity *  # Max effect 12pp
                  (1 + 0.5 * network_quality / sd(network_quality))  # Heterogeneous by networks
                )]
    
    # Comprehensive: large, persistent effects
    period_data[treatment_type == "comprehensive" & is_treatment_period, 
                employment_effect := (
                  0.25 * treatment_intensity *  # Max effect 25pp
                  pmin(1, periods_since_treatment / 2) *  # Builds up over 2 periods
                  (1 + 0.2 * (education == "basic"))  # Larger for low-educated
                )]
    
    # Set effect to 0 for control and pre-treatment
    period_data[treatment_type == "control" | is_pre_treatment, employment_effect := 0]
    
    # Final employment outcome
    period_data[, employment_rate := pmax(0, pmin(1, base_employment + employment_effect))]
    
    # Generate other employment outcomes
    # Contract quality (0-1 scale)
    period_data[, contract_quality := pmax(0, pmin(1, 
      0.6 + 0.3 * employment_rate + 0.2 * (education == "tertiary") +
      0.1 * ability + 0.5 * employment_effect + rnorm(.N, 0, 0.2)
    ))]
    
    # Monthly wage (conditional on employment)
    period_data[, monthly_wage := ifelse(employment_rate > runif(.N),
      pmax(800, baseline_wage + 200 * employment_effect + 
           100 * (education == "tertiary") + 50 * ability + rnorm(.N, 0, 300)),
      NA_real_
    )]
    
    # Employment stability (duration of current contract)
    period_data[, stability_index := pmax(0, pmin(1,
      0.5 + 0.4 * employment_rate + 0.2 * contract_quality + 
      0.3 * employment_effect + rnorm(.N, 0, 0.2)
    ))]
    
    panel_data <- rbind(panel_data, period_data)
  }
  
  # Add realistic contract type information
  panel_data[, COD_TIPOLOGIA_CONTRATTUALE := 
    ifelse(employment_rate > runif(.N),
           sample(c("A.01.00", "A.03.00", "A.03.01", "C.01.00", "A.07.00"), 
                  .N, replace = TRUE,
                  prob = c(0.3, 0.25, 0.15, 0.2, 0.1)),
           NA_character_)]
  
  # Create date variables
  period_data[, `:=`(
    inizio = as.Date("2020-01-01") + (period - 1) * 90,  # Quarterly data
    fine = as.Date("2020-01-01") + period * 90 - 1,
    durata = 90
  )]
  
  # Add unique identifiers
  panel_data[, over_id := .I]
  panel_data[, event_period := ifelse(post_treatment == 0, "pre", "post")]
  
  cat("\nPanel data structure:\n")
  cat("Total observations:", nrow(panel_data), "\n")
  cat("Individuals:", length(unique(panel_data$cf)), "\n")
  cat("Time periods:", length(unique(panel_data$period)), "\n")
  cat("Treatment types:", paste(unique(panel_data$treatment_type), collapse = ", "), "\n")
  
  return(panel_data[order(cf, period)])
}

# Generate the multi-treatment dataset
employment_data <- generate_multi_treatment_data(n_individuals = 1500, 
                                               n_time_periods = 8, 
                                               treatment_start_period = 4)

# Display first few observations
cat("\nFirst few observations:\n")
print(head(employment_data[, .(cf, period, treatment_type, treatment_intensity, 
                              employment_rate, contract_quality, monthly_wage)], 10))
```

## Exploratory Data Analysis

Before diving into causal inference, let's explore the patterns in our multi-treatment data:

```{r exploratory-analysis}
# Treatment assignment balance
cat("=== TREATMENT ASSIGNMENT ANALYSIS ===\n\n")

# Overall treatment distribution
treatment_summary <- employment_data[period == 1, .(
  count = .N,
  pct = round(100 * .N / nrow(employment_data[period == 1]), 1),
  mean_age = round(mean(age), 1),
  pct_basic_edu = round(100 * mean(education == "basic"), 1),
  mean_baseline_employment = round(mean(baseline_employment_rate), 3),
  mean_treatment_intensity = round(mean(treatment_intensity), 3)
), by = treatment_type][order(-count)]

cat("Treatment group characteristics:\n")
print(treatment_summary)

# Pre-treatment outcome trends
pre_treatment_trends <- employment_data[post_treatment == 0, .(
  mean_employment = mean(employment_rate, na.rm = TRUE),
  mean_contract_quality = mean(contract_quality, na.rm = TRUE),
  mean_wage = mean(monthly_wage, na.rm = TRUE),
  sd_employment = sd(employment_rate, na.rm = TRUE)
), by = .(treatment_type, period)]

cat("\nPre-treatment outcome trends:\n")
print(pre_treatment_trends[order(treatment_type, period)])

# Visualize pre-treatment trends
trend_plot <- ggplot(pre_treatment_trends, 
                     aes(x = period, y = mean_employment, color = treatment_type)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_color_viridis_d(name = "Treatment Type") +
  labs(
    title = "Pre-Treatment Employment Rate Trends by Treatment Group",
    subtitle = "Assessing parallel trends assumption",
    x = "Period",
    y = "Mean Employment Rate"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

print(trend_plot)

# Treatment intensity distribution
intensity_plot <- employment_data[period == 1 & treatment_type != "control", ] %>%
  ggplot(aes(x = treatment_intensity, fill = treatment_type)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity") +
  facet_wrap(~treatment_type, scales = "free_y") +
  scale_fill_viridis_d() +
  labs(
    title = "Treatment Intensity Distribution by Treatment Type",
    x = "Treatment Intensity",
    y = "Count"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

print(intensity_plot)
```

# Generalized Difference-in-Differences

## Multiple Treatment Groups DiD

The first approach for handling multiple treatments is to extend the standard DiD framework to accommodate multiple treatment groups and potentially multiple time periods.

```{r multiple-did-setup}
cat("=== MULTIPLE TREATMENT GROUPS DIFFERENCE-IN-DIFFERENCES ===\n\n")

# Prepare data for multiple treatment DiD
# Create binary indicators for each treatment type
did_data <- copy(employment_data)

# Create treatment dummies
treatment_types <- c("job_training", "wage_subsidy", "placement_assistance", "comprehensive")
for (treatment in treatment_types) {
  col_name <- paste0("treated_", gsub("_", "", treatment))
  did_data[, (col_name) := as.numeric(treatment_type == treatment)]
}

# Create interaction terms (treatment × post)
for (treatment in treatment_types) {
  treat_col <- paste0("treated_", gsub("_", "", treatment))
  interact_col <- paste0(treat_col, "_post")
  did_data[, (interact_col) := get(treat_col) * post_treatment]
}

cat("Multiple treatment DiD data structure:\n")
cat("Observations:", nrow(did_data), "\n")
cat("Treatment columns created:", sum(grepl("treated_", names(did_data))), "\n")
cat("Interaction columns created:", sum(grepl("_post", names(did_data))), "\n\n")

# Run multiple treatment DiD using longworkR functions
# First, prepare the data in the format expected by difference_in_differences()

# Create outcome variables list
outcome_vars <- c("employment_rate", "contract_quality", "monthly_wage", "stability_index")

# Prepare treatment indicators
did_data[, is_treated := as.numeric(treatment_type != "control")]

# Display sample of prepared data
cat("Sample of prepared DiD data:\n")
print(head(did_data[, .(cf, period, treatment_type, is_treated, post_treatment, 
                       employment_rate, contract_quality)], 8))
```

### Basic Multiple Treatment DiD

```{r basic-multiple-did}
# Run basic multiple treatment DiD
tryCatch({
  # Basic DiD with longworkR
  basic_multi_did <- difference_in_differences(
    data = did_data,
    outcome_vars = c("employment_rate", "contract_quality"),
    treatment_var = "is_treated",
    time_var = "post_treatment",
    id_var = "cf",
    control_vars = c("age", "baseline_employment_rate"),
    fixed_effects = "both",
    verbose = TRUE
  )
  
  cat("Basic multiple treatment DiD completed successfully\n")
  
  if (!is.null(basic_multi_did$summary_table)) {
    cat("\nBasic DiD Results:\n")
    print(basic_multi_did$summary_table)
  }
  
}, error = function(e) {
  cat("Error in basic multiple treatment DiD:", e$message, "\n")
  
  # Create manual DiD estimation as fallback
  cat("Creating manual DiD estimation...\n")
  
  # Manual DiD estimation for multiple outcomes
  did_results <- list()
  
  for (outcome in c("employment_rate", "contract_quality")) {
    if (outcome %in% names(did_data)) {
      # Calculate group means
      group_means <- did_data[!is.na(get(outcome)), .(
        mean_outcome = mean(get(outcome), na.rm = TRUE),
        n_obs = .N
      ), by = .(treatment_type, post_treatment)]
      
      cat(sprintf("\n%s - Group means:\n", outcome))
      print(group_means)
      
      # Calculate DiD estimates for each treatment vs control
      control_pre <- group_means[treatment_type == "control" & post_treatment == 0, mean_outcome]
      control_post <- group_means[treatment_type == "control" & post_treatment == 1, mean_outcome]
      control_change <- control_post - control_pre
      
      treatment_effects <- list()
      
      for (treat_type in treatment_types) {
        treat_pre <- group_means[treatment_type == treat_type & post_treatment == 0, mean_outcome]
        treat_post <- group_means[treatment_type == treat_type & post_treatment == 1, mean_outcome]
        
        if (length(treat_pre) > 0 && length(treat_post) > 0) {
          treat_change <- treat_post - treat_pre
          did_estimate <- treat_change - control_change
          
          treatment_effects[[treat_type]] <- list(
            pre_mean = treat_pre,
            post_mean = treat_post,
            change = treat_change,
            did_estimate = did_estimate
          )
          
          cat(sprintf("  %s: %.4f (change: %.4f, control change: %.4f)\n", 
                     treat_type, did_estimate, treat_change, control_change))
        }
      }
      
      did_results[[outcome]] <- treatment_effects
    }
  }
  
  basic_multi_did <- list(manual_results = did_results)
})

# Create visualization of multiple treatment effects
create_multi_treatment_plot <- function(data, outcome_var, title_suffix = "") {
  
  if (!outcome_var %in% names(data)) {
    cat("Outcome variable", outcome_var, "not found in data\n")
    return(NULL)
  }
  
  # Calculate means by treatment and time
  plot_data <- data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE),
    se_outcome = sd(get(outcome_var), na.rm = TRUE) / sqrt(.N),
    n_obs = .N
  ), by = .(treatment_type, period, post_treatment)]
  
  # Create the plot
  p <- ggplot(plot_data, aes(x = period, y = mean_outcome, color = treatment_type)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = 3.5, linetype = "dashed", alpha = 0.7) +
    scale_color_viridis_d(name = "Treatment Type") +
    labs(
      title = paste("Multiple Treatment Effects:", outcome_var, title_suffix),
      subtitle = "Dashed line indicates treatment start",
      x = "Period",
      y = paste("Mean", tools::toTitleCase(gsub("_", " ", outcome_var)))
    ) +
    theme_minimal() +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 12))
  
  return(p)
}

# Create plots for multiple outcomes
employment_plot <- create_multi_treatment_plot(did_data, "employment_rate")
if (!is.null(employment_plot)) print(employment_plot)

quality_plot <- create_multi_treatment_plot(did_data, "contract_quality")
if (!is.null(quality_plot)) print(quality_plot)
```

### Treatment-Specific Analysis

Now let's conduct pairwise comparisons between each treatment and the control group:

```{r treatment-specific-analysis}
cat("=== TREATMENT-SPECIFIC PAIRWISE ANALYSIS ===\n\n")

# Function to run pairwise DiD
run_pairwise_did <- function(data, treatment_type_focus, outcome_vars) {
  
  # Filter data to include only focal treatment and control
  pairwise_data <- data[treatment_type %in% c("control", treatment_type_focus)]
  
  if (nrow(pairwise_data) == 0) {
    cat("No data available for treatment:", treatment_type_focus, "\n")
    return(NULL)
  }
  
  # Create binary treatment indicator
  pairwise_data[, is_focal_treatment := as.numeric(treatment_type == treatment_type_focus)]
  
  cat(sprintf("Analyzing %s vs Control:\n", treatment_type_focus))
  cat(sprintf("  Observations: %d\n", nrow(pairwise_data)))
  cat(sprintf("  Treatment group size: %d\n", sum(pairwise_data$is_focal_treatment)))
  cat(sprintf("  Control group size: %d\n", sum(1 - pairwise_data$is_focal_treatment)))
  
  # Run DiD analysis
  tryCatch({
    pairwise_results <- difference_in_differences(
      data = pairwise_data,
      outcome_vars = outcome_vars[outcome_vars %in% names(pairwise_data)],
      treatment_var = "is_focal_treatment",
      time_var = "post_treatment",
      id_var = "cf",
      control_vars = c("age", "baseline_employment_rate"),
      fixed_effects = "both",
      verbose = FALSE
    )
    
    return(list(
      treatment_type = treatment_type_focus,
      results = pairwise_results,
      n_treated = sum(pairwise_data$is_focal_treatment),
      n_control = sum(1 - pairwise_data$is_focal_treatment)
    ))
    
  }, error = function(e) {
    cat("Error in pairwise DiD for", treatment_type_focus, ":", e$message, "\n")
    
    # Manual calculation as fallback
    manual_results <- list()
    
    for (outcome in outcome_vars[outcome_vars %in% names(pairwise_data)]) {
      group_means <- pairwise_data[!is.na(get(outcome)), .(
        mean_outcome = mean(get(outcome), na.rm = TRUE)
      ), by = .(is_focal_treatment, post_treatment)]
      
      if (nrow(group_means) == 4) {  # Should have 4 combinations
        control_pre <- group_means[is_focal_treatment == 0 & post_treatment == 0, mean_outcome]
        control_post <- group_means[is_focal_treatment == 0 & post_treatment == 1, mean_outcome]
        treat_pre <- group_means[is_focal_treatment == 1 & post_treatment == 0, mean_outcome]
        treat_post <- group_means[is_focal_treatment == 1 & post_treatment == 1, mean_outcome]
        
        did_estimate <- (treat_post - treat_pre) - (control_post - control_pre)
        
        manual_results[[outcome]] <- list(
          did_estimate = did_estimate,
          control_change = control_post - control_pre,
          treatment_change = treat_post - treat_pre
        )
      }
    }
    
    return(list(
      treatment_type = treatment_type_focus,
      manual_results = manual_results,
      n_treated = sum(pairwise_data$is_focal_treatment),
      n_control = sum(1 - pairwise_data$is_focal_treatment)
    ))
  })
}

# Run pairwise analysis for each treatment type
pairwise_results <- list()
outcomes_to_analyze <- c("employment_rate", "contract_quality", "stability_index")

for (treatment in treatment_types) {
  result <- run_pairwise_did(did_data, treatment, outcomes_to_analyze)
  if (!is.null(result)) {
    pairwise_results[[treatment]] <- result
  }
}

# Summarize pairwise results
cat("\n=== PAIRWISE DiD RESULTS SUMMARY ===\n\n")

pairwise_summary <- data.table()

for (treatment in names(pairwise_results)) {
  result <- pairwise_results[[treatment]]
  
  if ("results" %in% names(result) && !is.null(result$results$summary_table)) {
    # Extract from longworkR results
    summary_table <- result$results$summary_table
    if (inherits(summary_table, "data.table") || is.data.frame(summary_table)) {
      temp_summary <- as.data.table(summary_table)
      temp_summary[, treatment_type := treatment]
      temp_summary[, n_treated := result$n_treated]
      temp_summary[, n_control := result$n_control]
      pairwise_summary <- rbind(pairwise_summary, temp_summary, fill = TRUE)
    }
  } else if ("manual_results" %in% names(result)) {
    # Extract from manual results
    for (outcome in names(result$manual_results)) {
      outcome_result <- result$manual_results[[outcome]]
      temp_row <- data.table(
        outcome = outcome,
        estimate = outcome_result$did_estimate,
        treatment_type = treatment,
        n_treated = result$n_treated,
        n_control = result$n_control
      )
      pairwise_summary <- rbind(pairwise_summary, temp_row, fill = TRUE)
    }
  }
}

if (nrow(pairwise_summary) > 0) {
  cat("Pairwise DiD Results:\n")
  print(pairwise_summary[, .(treatment_type, outcome, estimate, n_treated, n_control)])
  
  # Create coefficient plot
  if ("estimate" %in% names(pairwise_summary) && "outcome" %in% names(pairwise_summary)) {
    coef_plot <- ggplot(pairwise_summary, aes(x = treatment_type, y = estimate, fill = outcome)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
      scale_fill_viridis_d(name = "Outcome") +
      labs(
        title = "Treatment-Specific DiD Estimates",
        subtitle = "Pairwise comparisons vs. Control group",
        x = "Treatment Type",
        y = "DiD Estimate"
      ) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "bottom")
    
    print(coef_plot)
  }
} else {
  cat("No pairwise results available for summary\n")
}
```

## Staggered Treatment Adoption

Many employment programs have staggered rollouts. Let's analyze this scenario:

```{r staggered-treatment}
cat("=== STAGGERED TREATMENT ADOPTION ANALYSIS ===\n\n")

# Create staggered treatment timing
staggered_data <- copy(employment_data)

# Assign different treatment start times by region
staggered_data[region == "north", treatment_start := 3]
staggered_data[region == "center", treatment_start := 4] 
staggered_data[region == "south", treatment_start := 5]
staggered_data[region == "islands", treatment_start := 6]

# Update post_treatment indicator based on staggered timing
staggered_data[, post_treatment_staggered := as.numeric(period >= treatment_start)]

# Create relative time to treatment
staggered_data[, relative_period := period - treatment_start]

# Only keep observations within reasonable window around treatment
staggered_data <- staggered_data[relative_period >= -3 & relative_period <= 4]

cat("Staggered treatment structure:\n")
staggered_summary <- staggered_data[, .(
  n_obs = .N,
  n_individuals = uniqueN(cf),
  treatment_start = first(treatment_start),
  n_treated = sum(treatment_type != "control")
), by = region]

print(staggered_summary)

# Event study analysis for staggered adoption
event_study_data <- staggered_data[treatment_type != "control"]  # Focus on treated units

if (nrow(event_study_data) > 0) {
  
  # Calculate event study coefficients manually
  # (This is a simplified version - real analysis would use proper event study methods)
  
  event_coefficients <- event_study_data[, .(
    mean_employment = mean(employment_rate, na.rm = TRUE),
    mean_contract_quality = mean(contract_quality, na.rm = TRUE),
    n_obs = .N
  ), by = relative_period]
  
  # Reference period (period -1)
  if (-1 %in% event_coefficients$relative_period) {
    ref_employment <- event_coefficients[relative_period == -1, mean_employment]
    ref_quality <- event_coefficients[relative_period == -1, mean_contract_quality]
    
    event_coefficients[, employment_effect := mean_employment - ref_employment]
    event_coefficients[, quality_effect := mean_contract_quality - ref_quality]
    
    cat("\nEvent Study Coefficients (relative to period -1):\n")
    print(event_coefficients[order(relative_period), 
                           .(relative_period, employment_effect, quality_effect, n_obs)])
    
    # Create event study plot
    event_plot_data <- melt(event_coefficients[, .(relative_period, employment_effect, quality_effect)],
                           id.vars = "relative_period",
                           variable.name = "outcome",
                           value.name = "effect")
    
    event_plot <- ggplot(event_plot_data, aes(x = relative_period, y = effect, color = outcome)) +
      geom_line(size = 1) +
      geom_point(size = 2) +
      geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.7) +
      geom_vline(xintercept = -0.5, linetype = "dotted", alpha = 0.7) +
      scale_color_viridis_d(name = "Outcome", 
                           labels = c("Employment Rate", "Contract Quality")) +
      labs(
        title = "Event Study: Treatment Effects Over Time",
        subtitle = "Relative to treatment start (vertical line at period 0)",
        x = "Relative Period (Treatment Start = 0)",
        y = "Treatment Effect"
      ) +
      theme_minimal() +
      theme(legend.position = "bottom")
    
    print(event_plot)
  }
} else {
  cat("No treated units available for event study analysis\n")
}
```

# Propensity Score Methods for Multiple Treatments

## Generalized Propensity Score Matching

When dealing with multiple treatments, we need to extend propensity score methods to handle the multinomial treatment assignment.

```{r generalized-propensity-score}
cat("=== GENERALIZED PROPENSITY SCORE MATCHING ===\n\n")

# Prepare data for propensity score analysis
# Use baseline (pre-treatment) characteristics only
baseline_data <- employment_data[period == 1]  # Use first period as baseline

# Create comprehensive covariate set for propensity score estimation
covariates <- c("age", "education", "region", "baseline_employment_rate", 
               "baseline_wage", "previous_unemployment_duration", "sector_experience")

# Check covariate availability and create numeric versions
cat("Covariate preparation:\n")
for (var in covariates) {
  if (var %in% names(baseline_data)) {
    cat(sprintf("  %s: available (%s)\n", var, class(baseline_data[[var]])[1]))
  } else {
    cat(sprintf("  %s: missing\n", var))
  }
}

# Create numeric versions of categorical variables for propensity score estimation
propensity_data <- copy(baseline_data)

# Convert categorical variables to dummy variables
propensity_data[, edu_secondary := as.numeric(education == "secondary")]
propensity_data[, edu_tertiary := as.numeric(education == "tertiary")]
propensity_data[, region_center := as.numeric(region == "center")]
propensity_data[, region_south := as.numeric(region == "south")]
propensity_data[, region_islands := as.numeric(region == "islands")]
propensity_data[, sector_services := as.numeric(sector_experience == "services")]
propensity_data[, sector_construction := as.numeric(sector_experience == "construction")]
propensity_data[, sector_other := as.numeric(sector_experience == "other")]

# Standardize continuous variables
continuous_vars <- c("age", "baseline_employment_rate", "baseline_wage", "previous_unemployment_duration")
for (var in continuous_vars) {
  if (var %in% names(propensity_data)) {
    mean_val <- mean(propensity_data[[var]], na.rm = TRUE)
    sd_val <- sd(propensity_data[[var]], na.rm = TRUE)
    new_var <- paste0(var, "_std")
    propensity_data[, (new_var) := (get(var) - mean_val) / sd_val]
  }
}

# Estimate generalized propensity scores using multinomial logit
# (Simplified implementation - in practice, use nnet::multinom or similar)

cat("\nEstimating generalized propensity scores...\n")

# Create treatment type as factor
propensity_data[, treatment_factor := factor(treatment_type, 
                                           levels = c("control", treatment_types))]

# Calculate propensity scores manually using simple approach
# (In practice, use proper multinomial logit estimation)
calculate_simple_propensity <- function(data) {
  
  # Count-based propensity scores (naive approach for demonstration)
  treatment_counts <- table(data$treatment_type)
  total_n <- nrow(data)
  
  propensity_scores <- data.table(
    treatment_type = names(treatment_counts),
    raw_propensity = as.numeric(treatment_counts / total_n)
  )
  
  # Add some variation based on covariates (simplified)
  result_data <- copy(data)
  
  for (treat_type in names(treatment_counts)) {
    prop_var <- paste0("prop_", gsub("_", "", treat_type))
    base_prop <- treatment_counts[treat_type] / total_n
    
    # Add covariate-based variation (simplified)
    if (treat_type == "job_training") {
      result_data[, (prop_var) := pmax(0.01, pmin(0.99, 
        base_prop + 0.1 * (education == "basic") - 0.05 * age_std))]
    } else if (treat_type == "wage_subsidy") {
      result_data[, (prop_var) := pmax(0.01, pmin(0.99, 
        base_prop + 0.08 * (baseline_employment_rate < 0.4) - 0.03 * baseline_wage_std))]
    } else if (treat_type == "placement_assistance") {
      result_data[, (prop_var) := pmax(0.01, pmin(0.99, 
        base_prop + 0.06 * sector_services - 0.02 * age_std))]
    } else if (treat_type == "comprehensive") {
      result_data[, (prop_var) := pmax(0.01, pmin(0.99, 
        base_prop + 0.12 * (education == "basic") + 0.05 * (previous_unemployment_duration > 365)))]
    } else {  # control
      result_data[, (prop_var) := base_prop]
    }
  }
  
  return(result_data)
}

propensity_results <- calculate_simple_propensity(propensity_data)

cat("Propensity score estimation completed\n")

# Display propensity score distributions
prop_vars <- grep("^prop_", names(propensity_results), value = TRUE)
if (length(prop_vars) > 0) {
  cat("\nPropensity score summary:\n")
  for (prop_var in prop_vars[1:min(3, length(prop_vars))]) {
    cat(sprintf("%s: mean=%.3f, sd=%.3f\n", 
               prop_var, 
               mean(propensity_results[[prop_var]], na.rm = TRUE),
               sd(propensity_results[[prop_var]], na.rm = TRUE)))
  }
}

# Assess covariate balance before matching
assess_balance <- function(data, treatment_var, covariates) {
  
  balance_results <- data.table()
  
  for (cov in covariates) {
    if (cov %in% names(data)) {
      
      if (is.numeric(data[[cov]])) {
        # For numeric variables, calculate standardized differences
        cov_summary <- data[, .(
          mean_val = mean(get(cov), na.rm = TRUE),
          sd_val = sd(get(cov), na.rm = TRUE),
          n_obs = sum(!is.na(get(cov)))
        ), by = c(treatment_var)]
        
        if (nrow(cov_summary) >= 2) {
          control_mean <- cov_summary[get(treatment_var) == "control", mean_val]
          control_sd <- cov_summary[get(treatment_var) == "control", sd_val]
          
          for (treat_type in unique(cov_summary[[treatment_var]])) {
            if (treat_type != "control") {
              treat_mean <- cov_summary[get(treatment_var) == treat_type, mean_val]
              
              if (length(control_mean) > 0 && length(treat_mean) > 0 && control_sd > 0) {
                std_diff <- (treat_mean - control_mean) / control_sd
                
                balance_results <- rbind(balance_results, data.table(
                  covariate = cov,
                  treatment_type = treat_type,
                  control_mean = control_mean,
                  treatment_mean = treat_mean,
                  std_diff = std_diff,
                  variable_type = "numeric"
                ))
              }
            }
          }
        }
      } else {
        # For categorical variables, calculate proportions
        prop_table <- data[, .N, by = c(treatment_var, cov)][, 
                          prop := N / sum(N), by = c(treatment_var)]
        
        balance_results <- rbind(balance_results, data.table(
          covariate = cov,
          treatment_type = "categorical",
          control_mean = NA,
          treatment_mean = NA,
          std_diff = NA,
          variable_type = "categorical"
        ))
      }
    }
  }
  
  return(balance_results)
}

# Assess balance before matching
pre_match_balance <- assess_balance(propensity_results, "treatment_type", 
                                  continuous_vars)

if (nrow(pre_match_balance) > 0) {
  cat("\nCovariate balance before matching (standardized differences):\n")
  print(pre_match_balance[!is.na(std_diff), 
                        .(covariate, treatment_type, std_diff)][order(abs(std_diff), decreasing = TRUE)])
  
  # Create balance plot
  if (sum(!is.na(pre_match_balance$std_diff)) > 0) {
    balance_plot <- ggplot(pre_match_balance[!is.na(std_diff)], 
                          aes(x = reorder(paste(treatment_type, covariate), abs(std_diff)), 
                              y = std_diff, fill = treatment_type)) +
      geom_col(alpha = 0.8) +
      geom_hline(yintercept = c(-0.1, 0.1), linetype = "dashed", alpha = 0.7) +
      coord_flip() +
      scale_fill_viridis_d() +
      labs(
        title = "Covariate Balance Before Matching",
        subtitle = "Standardized differences (dashed lines at ±0.1)",
        x = "Treatment-Covariate",
        y = "Standardized Difference"
      ) +
      theme_minimal() +
      theme(legend.position = "bottom")
    
    print(balance_plot)
  }
}
```

### Matching Implementation

```{r matching-implementation}
cat("=== IMPLEMENTING PROPENSITY SCORE MATCHING ===\n\n")

# Try to use longworkR matching functions if available
tryCatch({
  
  # Prepare data for matching using longworkR functions
  # Create binary treatment indicators for each type
  matching_data <- copy(propensity_results)
  
  # Create separate matching analyses for each treatment vs. control
  matching_results <- list()
  
  for (focal_treatment in treatment_types[1:2]) {  # Limit to first 2 for demo
    
    cat(sprintf("Matching analysis: %s vs Control\n", focal_treatment))
    
    # Filter data for binary comparison
    binary_data <- matching_data[treatment_type %in% c("control", focal_treatment)]
    binary_data[, is_treated_binary := as.numeric(treatment_type == focal_treatment)]
    
    # Prepare covariates for matching
    matching_covariates <- c("age_std", "baseline_employment_rate_std", 
                           "edu_secondary", "edu_tertiary", "region_center", "region_south")
    
    # Check covariate availability
    available_covariates <- intersect(matching_covariates, names(binary_data))
    
    if (length(available_covariates) >= 3 && nrow(binary_data) >= 20) {
      
      # Use propensity_score_matching function if available
      if (exists("propensity_score_matching") && is.function(propensity_score_matching)) {
        
        matching_result <- propensity_score_matching(
          data = binary_data,
          treatment_var = "is_treated_binary",
          matching_variables = available_covariates,
          method = "nearest",
          caliper = 0.1,
          replace = FALSE
        )
        
        matching_results[[focal_treatment]] <- matching_result
        cat(sprintf("  Matching completed for %s\n", focal_treatment))
        
      } else {
        
        # Manual nearest neighbor matching implementation
        cat(sprintf("  Implementing manual matching for %s\n", focal_treatment))
        
        treated_data <- binary_data[is_treated_binary == 1]
        control_data <- binary_data[is_treated_binary == 0]
        
        if (nrow(treated_data) > 0 && nrow(control_data) > 0) {
          
          # Calculate distances (simplified Euclidean distance)
          distances <- matrix(NA, nrow = nrow(treated_data), ncol = nrow(control_data))
          
          for (i in 1:nrow(treated_data)) {
            for (j in 1:nrow(control_data)) {
              
              # Calculate distance based on available covariates
              dist_components <- numeric(length(available_covariates))
              
              for (k in seq_along(available_covariates)) {
                cov <- available_covariates[k]
                if (cov %in% names(treated_data) && cov %in% names(control_data)) {
                  t_val <- treated_data[i, get(cov)]
                  c_val <- control_data[j, get(cov)]
                  if (!is.na(t_val) && !is.na(c_val)) {
                    dist_components[k] <- (t_val - c_val)^2
                  }
                }
              }
              
              distances[i, j] <- sqrt(sum(dist_components))
            }
          }
          
          # Find nearest matches
          matches <- data.table()
          
          for (i in 1:nrow(treated_data)) {
            if (!is.null(distances) && !is.na(distances[i, ])) {
              best_match_idx <- which.min(distances[i, ])
              if (length(best_match_idx) > 0) {
                matches <- rbind(matches, data.table(
                  treated_id = treated_data[i, cf],
                  control_id = control_data[best_match_idx, cf],
                  distance = distances[i, best_match_idx]
                ))
              }
            }
          }
          
          matching_results[[focal_treatment]] <- list(
            matches = matches,
            n_treated = nrow(treated_data),
            n_control = nrow(control_data),
            n_matched = nrow(matches)
          )
          
          cat(sprintf("  Manual matching: %d matches from %d treated units\n", 
                     nrow(matches), nrow(treated_data)))
        }
      }
      
    } else {
      cat(sprintf("  Insufficient data for matching %s (n=%d, covariates=%d)\n", 
                 focal_treatment, nrow(binary_data), length(available_covariates)))
    }
  }
  
}, error = function(e) {
  cat("Error in matching implementation:", e$message, "\n")
  matching_results <- list()
})

# Summarize matching results
if (length(matching_results) > 0) {
  cat("\n=== MATCHING RESULTS SUMMARY ===\n")
  
  for (treatment in names(matching_results)) {
    result <- matching_results[[treatment]]
    cat(sprintf("\n%s vs Control:\n", treatment))
    
    if ("matches" %in% names(result)) {
      cat(sprintf("  Matched pairs: %d\n", nrow(result$matches)))
      cat(sprintf("  Match rate: %.1f%%\n", 100 * nrow(result$matches) / result$n_treated))
      
      if (nrow(result$matches) > 0) {
        cat(sprintf("  Average distance: %.3f\n", mean(result$matches$distance, na.rm = TRUE)))
      }
    } else if ("n_matched" %in% names(result)) {
      cat(sprintf("  Matches created: %d out of %d treated\n", result$n_matched, result$n_treated))
    }
  }
} else {
  cat("No matching results available\n")
}
```

# Dose-Response Analysis

## Continuous Treatment Intensity

Employment programs often have varying intensities. Let's analyze the dose-response relationship:

```{r dose-response}
cat("=== DOSE-RESPONSE ANALYSIS ===\n\n")

# Focus on treated units only for dose-response analysis
dose_data <- employment_data[treatment_type != "control" & !is.na(treatment_intensity)]

cat("Dose-response data structure:\n")
cat("Observations:", nrow(dose_data), "\n")
cat("Individuals:", length(unique(dose_data$cf)), "\n")
cat("Treatment intensity range:", 
    sprintf("%.2f - %.2f", min(dose_data$treatment_intensity), max(dose_data$treatment_intensity)), "\n")

# Create intensity bins for analysis
dose_data[, intensity_bin := cut(treatment_intensity, 
                               breaks = c(0, 0.4, 0.7, 1.0),
                               labels = c("Low", "Medium", "High"),
                               include.lowest = TRUE)]

cat("\nTreatment intensity distribution:\n")
print(table(dose_data$intensity_bin, dose_data$treatment_type))

# Calculate dose-response relationships
dose_response_analysis <- function(data, outcome_var, treatment_var = "treatment_intensity") {
  
  if (!outcome_var %in% names(data) || !treatment_var %in% names(data)) {
    cat("Missing variables for dose-response analysis\n")
    return(NULL)
  }
  
  # Pre-post comparison by intensity level
  dose_results <- data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE),
    sd_outcome = sd(get(outcome_var), na.rm = TRUE),
    n_obs = .N
  ), by = .(intensity_bin, post_treatment, treatment_type)]
  
  # Calculate dose-response effects (post - pre)
  pre_outcomes <- dose_results[post_treatment == 0, 
                             .(intensity_bin, treatment_type, pre_mean = mean_outcome)]
  post_outcomes <- dose_results[post_treatment == 1, 
                              .(intensity_bin, treatment_type, post_mean = mean_outcome)]
  
  dose_effects <- merge(pre_outcomes, post_outcomes, 
                       by = c("intensity_bin", "treatment_type"), all = TRUE)
  dose_effects[, dose_effect := post_mean - pre_mean]
  
  return(list(
    raw_results = dose_results,
    dose_effects = dose_effects,
    outcome = outcome_var
  ))
}

# Analyze dose-response for multiple outcomes
outcomes_for_dose <- c("employment_rate", "contract_quality", "stability_index")
dose_analyses <- list()

for (outcome in outcomes_for_dose) {
  result <- dose_response_analysis(dose_data, outcome)
  if (!is.null(result)) {
    dose_analyses[[outcome]] <- result
    
    cat(sprintf("\nDose-response results for %s:\n", outcome))
    if (nrow(result$dose_effects) > 0) {
      print(result$dose_effects[, .(treatment_type, intensity_bin, dose_effect)][
        !is.na(dose_effect)][order(treatment_type, intensity_bin)])
    }
  }
}

# Create dose-response visualizations
if (length(dose_analyses) > 0) {
  
  # Combined dose-response plot
  all_effects <- data.table()
  
  for (outcome in names(dose_analyses)) {
    result <- dose_analyses[[outcome]]
    if (!is.null(result$dose_effects) && nrow(result$dose_effects) > 0) {
      temp_effects <- result$dose_effects[!is.na(dose_effect)]
      temp_effects[, outcome_var := outcome]
      all_effects <- rbind(all_effects, temp_effects, fill = TRUE)
    }
  }
  
  if (nrow(all_effects) > 0) {
    
    dose_plot <- ggplot(all_effects, aes(x = intensity_bin, y = dose_effect, 
                                       fill = treatment_type)) +
      geom_col(position = "dodge", alpha = 0.8) +
      facet_wrap(~outcome_var, scales = "free_y") +
      geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.7) +
      scale_fill_viridis_d(name = "Treatment Type") +
      labs(
        title = "Dose-Response Analysis: Treatment Effects by Intensity",
        subtitle = "Change from pre-treatment to post-treatment period",
        x = "Treatment Intensity Level",
        y = "Treatment Effect"
      ) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "bottom")
    
    print(dose_plot)
    
    # Create continuous dose-response curves
    continuous_dose_data <- dose_data[!is.na(employment_rate), .(
      treatment_intensity = round(treatment_intensity, 2),
      employment_effect = employment_rate - mean(employment_rate[post_treatment == 0], na.rm = TRUE),
      post_treatment,
      treatment_type
    ), by = cf]
    
    # Smooth dose-response relationship
    if (nrow(continuous_dose_data[post_treatment == 1]) > 20) {
      
      continuous_plot <- ggplot(continuous_dose_data[post_treatment == 1], 
                               aes(x = treatment_intensity, y = employment_effect)) +
        geom_point(alpha = 0.4, size = 1) +
        geom_smooth(method = "loess", se = TRUE, color = "blue") +
        facet_wrap(~treatment_type, scales = "free") +
        geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.7) +
        labs(
          title = "Continuous Dose-Response Curves",
          subtitle = "Employment rate effect vs. treatment intensity",
          x = "Treatment Intensity",
          y = "Employment Effect"
        ) +
        theme_minimal()
      
      print(continuous_plot)
    }
  }
}

# Statistical tests for dose-response
cat("\n=== STATISTICAL TESTS FOR DOSE-RESPONSE ===\n\n")

# Test for linear dose-response relationship
for (treatment in treatment_types[1:2]) {  # Limit for demonstration
  
  treatment_data <- dose_data[treatment_type == treatment & post_treatment == 1]
  
  if (nrow(treatment_data) >= 10) {
    
    cat(sprintf("Linear dose-response test for %s:\n", treatment))
    
    # Simple linear regression
    tryCatch({
      for (outcome in c("employment_rate", "contract_quality")) {
        if (outcome %in% names(treatment_data)) {
          
          # Remove NA values
          analysis_data <- treatment_data[!is.na(get(outcome)) & !is.na(treatment_intensity)]
          
          if (nrow(analysis_data) >= 5) {
            
            # Fit linear model
            model_formula <- as.formula(paste(outcome, "~ treatment_intensity"))
            lm_result <- lm(model_formula, data = analysis_data)
            
            coef_intensity <- coef(lm_result)["treatment_intensity"]
            p_val <- summary(lm_result)$coefficients["treatment_intensity", "Pr(>|t|)"]
            
            cat(sprintf("  %s: coefficient=%.4f, p-value=%.3f\n", 
                       outcome, coef_intensity, p_val))
          }
        }
      }
    }, error = function(e) {
      cat(sprintf("  Error in dose-response test: %s\n", e$message))
    })
    
    cat("\n")
  }
}
```

# Treatment Effect Heterogeneity

## Subgroup Analysis

Let's explore how treatment effects vary across different subgroups:

```{r heterogeneity-analysis}
cat("=== TREATMENT EFFECT HETEROGENEITY ANALYSIS ===\n\n")

# Define subgroups for heterogeneity analysis
heterogeneity_data <- copy(employment_data)

# Create subgroup indicators
heterogeneity_data[, `:=`(
  young_worker = as.numeric(age <= 30),
  low_educated = as.numeric(education == "basic"),
  high_unemployment_region = as.numeric(region %in% c("south", "islands")),
  low_baseline_employment = as.numeric(baseline_employment_rate <= 0.4),
  experienced_worker = as.numeric(age >= 45)
)]

subgroups <- c("young_worker", "low_educated", "high_unemployment_region", 
               "low_baseline_employment", "experienced_worker")

cat("Subgroup definitions:\n")
for (subgroup in subgroups) {
  n_in_subgroup <- sum(heterogeneity_data[period == 1, get(subgroup)])
  pct_in_subgroup <- 100 * mean(heterogeneity_data[period == 1, get(subgroup)])
  cat(sprintf("  %s: %d individuals (%.1f%%)\n", subgroup, n_in_subgroup, pct_in_subgroup))
}

# Analyze treatment effects by subgroup
subgroup_analysis <- function(data, treatment_focus, outcome_var, subgroup_var) {
  
  # Filter data for focal treatment vs control
  analysis_data <- data[treatment_type %in% c("control", treatment_focus)]
  
  if (nrow(analysis_data) == 0 || !outcome_var %in% names(analysis_data) || 
      !subgroup_var %in% names(analysis_data)) {
    return(NULL)
  }
  
  # Calculate treatment effects by subgroup
  subgroup_results <- analysis_data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE),
    n_obs = .N
  ), by = .(get(subgroup_var), treatment_type, post_treatment)]
  
  setnames(subgroup_results, "get", subgroup_var)
  
  # Calculate DiD estimates by subgroup
  did_estimates <- data.table()
  
  for (subgroup_val in unique(subgroup_results[[subgroup_var]])) {
    
    subgroup_data <- subgroup_results[get(subgroup_var) == subgroup_val]
    
    # Check if we have all necessary combinations
    if (nrow(subgroup_data) == 4) {  # 2 treatments × 2 time periods
      
      control_pre <- subgroup_data[treatment_type == "control" & post_treatment == 0, mean_outcome]
      control_post <- subgroup_data[treatment_type == "control" & post_treatment == 1, mean_outcome]
      treat_pre <- subgroup_data[treatment_type == treatment_focus & post_treatment == 0, mean_outcome]
      treat_post <- subgroup_data[treatment_type == treatment_focus & post_treatment == 1, mean_outcome]
      
      if (length(control_pre) > 0 && length(control_post) > 0 && 
          length(treat_pre) > 0 && length(treat_post) > 0) {
        
        control_change <- control_post - control_pre
        treat_change <- treat_post - treat_pre
        did_estimate <- treat_change - control_change
        
        did_estimates <- rbind(did_estimates, data.table(
          subgroup_var = subgroup_var,
          subgroup_val = subgroup_val,
          treatment_type = treatment_focus,
          outcome = outcome_var,
          did_estimate = did_estimate,
          control_change = control_change,
          treatment_change = treat_change
        ))
      }
    }
  }
  
  return(did_estimates)
}

# Run subgroup analysis for key treatment-outcome combinations
heterogeneity_results <- data.table()

for (treatment in treatment_types[1:2]) {  # Limit for demonstration
  for (outcome in c("employment_rate", "contract_quality")) {
    for (subgroup in subgroups[1:3]) {  # Limit subgroups for demonstration
      
      result <- subgroup_analysis(heterogeneity_data, treatment, outcome, subgroup)
      
      if (!is.null(result) && nrow(result) > 0) {
        heterogeneity_results <- rbind(heterogeneity_results, result)
      }
    }
  }
}

# Display heterogeneity results
if (nrow(heterogeneity_results) > 0) {
  cat("\n=== HETEROGENEITY RESULTS ===\n\n")
  
  # Summary table
  het_summary <- heterogeneity_results[, .(
    subgroup_var, subgroup_val, treatment_type, outcome, did_estimate
  )][order(treatment_type, outcome, subgroup_var, subgroup_val)]
  
  cat("Treatment effect heterogeneity by subgroups:\n")
  print(het_summary)
  
  # Create heterogeneity visualization
  het_plot <- ggplot(heterogeneity_results, 
                    aes(x = factor(subgroup_val), y = did_estimate, 
                        fill = factor(subgroup_val))) +
    geom_col(alpha = 0.8) +
    facet_grid(outcome ~ paste(treatment_type, subgroup_var), 
               scales = "free", space = "free_x") +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.7) +
    scale_fill_viridis_d(name = "Subgroup") +
    labs(
      title = "Treatment Effect Heterogeneity Analysis",
      subtitle = "DiD estimates by subgroups (0 = not in subgroup, 1 = in subgroup)",
      x = "Subgroup Status",
      y = "DiD Estimate"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(size = 8),
          legend.position = "bottom")
  
  print(het_plot)
  
  # Test for significant heterogeneity
  cat("\n=== TESTS FOR HETEROGENEOUS TREATMENT EFFECTS ===\n\n")
  
  for (treatment in unique(heterogeneity_results$treatment_type)) {
    for (outcome in unique(heterogeneity_results$outcome)) {
      
      subset_results <- heterogeneity_results[
        treatment_type == treatment & outcome == outcome]
      
      if (nrow(subset_results) >= 4) {  # Need multiple subgroups
        
        cat(sprintf("%s - %s:\n", treatment, outcome))
        
        # Simple heterogeneity test (compare subgroup differences)
        het_test_data <- dcast(subset_results, 
                              subgroup_var ~ subgroup_val, 
                              value.var = "did_estimate")
        
        if (ncol(het_test_data) == 3 && "0" %in% names(het_test_data) && "1" %in% names(het_test_data)) {
          het_test_data[, difference := `1` - `0`]
          
          print(het_test_data[!is.na(difference), .(subgroup_var, difference)])
        }
        
        cat("\n")
      }
    }
  }
} else {
  cat("No heterogeneity results available\n")
}
```

# Advanced Methods and Extensions

## Machine Learning Approaches

Let's explore machine learning methods for heterogeneous treatment effects:

```{r machine-learning}
cat("=== MACHINE LEARNING FOR HETEROGENEOUS EFFECTS ===\n\n")

# Prepare data for machine learning analysis
ml_data <- copy(employment_data[period == 4])  # Use post-treatment period

# Create feature matrix
features <- c("age", "baseline_employment_rate", "baseline_wage", 
             "previous_unemployment_duration")

# Convert categorical variables
ml_data[, `:=`(
  edu_basic = as.numeric(education == "basic"),
  edu_secondary = as.numeric(education == "secondary"), 
  edu_tertiary = as.numeric(education == "tertiary"),
  region_north = as.numeric(region == "north"),
  region_center = as.numeric(region == "center"),
  region_south = as.numeric(region == "south"),
  region_islands = as.numeric(region == "islands"),
  sector_manufacturing = as.numeric(sector_experience == "manufacturing"),
  sector_services = as.numeric(sector_experience == "services"),
  sector_construction = as.numeric(sector_experience == "construction")
)]

# Comprehensive feature set
ml_features <- c(features, "edu_basic", "edu_secondary", "edu_tertiary",
                "region_center", "region_south", "region_islands",
                "sector_services", "sector_construction")

# Check feature availability
available_features <- intersect(ml_features, names(ml_data))
cat("Available features for ML analysis:", length(available_features), "\n")
cat("Features:", paste(available_features[1:8], collapse = ", "), "...\n\n")

# Implement simplified causal forest approach
# (In practice, use grf package for proper causal forest implementation)

implement_simple_causal_forest <- function(data, outcome_var, treatment_var, features) {
  
  # Remove missing values
  vars_to_check <- c(outcome_var, treatment_var, features)
  complete_data <- data[complete.cases(data[, ..vars_to_check])]
  
  if (nrow(complete_data) < 50) {
    cat("Insufficient complete cases for causal forest analysis\n")
    return(NULL)
  }
  
  cat(sprintf("Causal forest analysis with %d complete observations\n", nrow(complete_data)))
  
  # Simple heterogeneity analysis using interaction effects
  # Create treatment indicators for each type
  forest_results <- list()
  
  for (treatment in treatment_types[1:2]) {  # Limit for demonstration
    
    # Create binary treatment indicator
    forest_data <- copy(complete_data)
    forest_data[, binary_treatment := as.numeric(treatment_type == treatment)]
    
    if (sum(forest_data$binary_treatment) >= 10 && 
        sum(1 - forest_data$binary_treatment) >= 10) {
      
      # Simple linear model with interactions (proxy for causal forest)
      interaction_vars <- available_features[1:min(3, length(available_features))]
      
      tryCatch({
        # Create interaction terms
        interaction_formula <- paste(outcome_var, "~ binary_treatment * (", 
                                   paste(interaction_vars, collapse = " + "), ")")
        
        interaction_model <- lm(as.formula(interaction_formula), data = forest_data)
        
        # Extract interaction coefficients
        interaction_coefs <- coef(interaction_model)
        interaction_names <- names(interaction_coefs)[grepl(":", names(interaction_coefs))]
        
        if (length(interaction_names) > 0) {
          
          forest_results[[treatment]] <- list(
            model = interaction_model,
            interaction_effects = interaction_coefs[interaction_names],
            n_treated = sum(forest_data$binary_treatment),
            n_control = sum(1 - forest_data$binary_treatment)
          )
          
          cat(sprintf("  %s: %d interaction terms estimated\n", 
                     treatment, length(interaction_names)))
        }
        
      }, error = function(e) {
        cat(sprintf("  Error in %s analysis: %s\n", treatment, e$message))
      })
    }
  }
  
  return(forest_results)
}

# Run simplified causal forest analysis
if (length(available_features) >= 3) {
  
  forest_results <- implement_simple_causal_forest(
    ml_data, 
    "employment_rate", 
    "treatment_type", 
    available_features[1:5]  # Limit features for stability
  )
  
  if (length(forest_results) > 0) {
    cat("\n=== CAUSAL FOREST RESULTS (SIMPLIFIED) ===\n\n")
    
    for (treatment in names(forest_results)) {
      result <- forest_results[[treatment]]
      cat(sprintf("%s vs Control:\n", treatment))
      cat(sprintf("  Sample sizes: %d treated, %d control\n", 
                 result$n_treated, result$n_control))
      
      if (length(result$interaction_effects) > 0) {
        cat("  Key interaction effects:\n")
        sorted_effects <- sort(abs(result$interaction_effects), decreasing = TRUE)
        for (i in 1:min(3, length(sorted_effects))) {
          effect_name <- names(sorted_effects)[i]
          effect_size <- result$interaction_effects[effect_name]
          cat(sprintf("    %s: %.4f\n", effect_name, effect_size))
        }
      }
      cat("\n")
    }
  }
} else {
  cat("Insufficient features for machine learning analysis\n")
}
```

## Sensitivity Analysis and Robustness Checks

```{r sensitivity-analysis}
cat("=== SENSITIVITY ANALYSIS AND ROBUSTNESS CHECKS ===\n\n")

# 1. Alternative control groups
cat("1. ALTERNATIVE CONTROL GROUPS\n")

# Compare different treatment types as alternative controls
alternative_controls_analysis <- function(data, focal_treatment, alternative_control, outcome_var) {
  
  # Compare focal treatment vs alternative control (instead of true control)
  alt_data <- data[treatment_type %in% c(alternative_control, focal_treatment)]
  
  if (nrow(alt_data) == 0) return(NULL)
  
  # Create binary treatment indicator
  alt_data[, is_focal := as.numeric(treatment_type == focal_treatment)]
  
  # Calculate alternative DiD estimate
  alt_results <- alt_data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE)
  ), by = .(is_focal, post_treatment)]
  
  if (nrow(alt_results) == 4) {
    control_pre <- alt_results[is_focal == 0 & post_treatment == 0, mean_outcome]
    control_post <- alt_results[is_focal == 0 & post_treatment == 1, mean_outcome]
    treat_pre <- alt_results[is_focal == 1 & post_treatment == 0, mean_outcome]
    treat_post <- alt_results[is_focal == 1 & post_treatment == 1, mean_outcome]
    
    did_estimate <- (treat_post - treat_pre) - (control_post - control_pre)
    
    return(data.table(
      focal_treatment = focal_treatment,
      alternative_control = alternative_control,
      outcome = outcome_var,
      alternative_did = did_estimate
    ))
  }
  
  return(NULL)
}

# Run alternative control analysis
alt_control_results <- data.table()

for (focal_treat in treatment_types[1:2]) {
  for (alt_control in treatment_types[treatment_types != focal_treat][1:2]) {
    result <- alternative_controls_analysis(employment_data, focal_treat, alt_control, "employment_rate")
    if (!is.null(result)) {
      alt_control_results <- rbind(alt_control_results, result)
    }
  }
}

if (nrow(alt_control_results) > 0) {
  cat("Alternative control group results (employment_rate):\n")
  print(alt_control_results)
} else {
  cat("No alternative control results available\n")
}

# 2. Placebo tests
cat("\n2. PLACEBO TESTS\n")

# Test with fake treatment timing (pre-treatment periods only)
placebo_test <- function(data, treatment_focus, outcome_var, fake_treatment_period = 2) {
  
  # Use only pre-treatment data
  placebo_data <- data[period <= 3 & treatment_type %in% c("control", treatment_focus)]
  
  if (nrow(placebo_data) == 0) return(NULL)
  
  # Create fake post-treatment indicator
  placebo_data[, fake_post := as.numeric(period >= fake_treatment_period)]
  placebo_data[, is_treated_placebo := as.numeric(treatment_type == treatment_focus)]
  
  # Calculate placebo DiD
  placebo_results <- placebo_data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE)
  ), by = .(is_treated_placebo, fake_post)]
  
  if (nrow(placebo_results) == 4) {
    control_pre <- placebo_results[is_treated_placebo == 0 & fake_post == 0, mean_outcome]
    control_post <- placebo_results[is_treated_placebo == 0 & fake_post == 1, mean_outcome]
    treat_pre <- placebo_results[is_treated_placebo == 1 & fake_post == 0, mean_outcome]
    treat_post <- placebo_results[is_treated_placebo == 1 & fake_post == 1, mean_outcome]
    
    placebo_did <- (treat_post - treat_pre) - (control_post - control_pre)
    
    return(data.table(
      treatment_type = treatment_focus,
      outcome = outcome_var,
      placebo_estimate = placebo_did,
      fake_period = fake_treatment_period
    ))
  }
  
  return(NULL)
}

# Run placebo tests
placebo_results <- data.table()

for (treatment in treatment_types[1:2]) {
  result <- placebo_test(employment_data, treatment, "employment_rate", 2)
  if (!is.null(result)) {
    placebo_results <- rbind(placebo_results, result)
  }
}

if (nrow(placebo_results) > 0) {
  cat("Placebo test results (should be close to zero):\n")
  print(placebo_results[, .(treatment_type, placebo_estimate)])
} else {
  cat("No placebo test results available\n")
}

# 3. Exclude certain periods
cat("\n3. ROBUSTNESS TO PERIOD EXCLUSION\n")

exclusion_test <- function(data, treatment_focus, outcome_var, exclude_period) {
  
  # Exclude specific period
  robust_data <- data[period != exclude_period & 
                     treatment_type %in% c("control", treatment_focus)]
  
  if (nrow(robust_data) == 0) return(NULL)
  
  robust_data[, is_treated_robust := as.numeric(treatment_type == treatment_focus)]
  
  # Recalculate post-treatment (adjust if necessary)
  robust_data[, post_robust := post_treatment]
  
  # Calculate robust DiD
  robust_results <- robust_data[!is.na(get(outcome_var)), .(
    mean_outcome = mean(get(outcome_var), na.rm = TRUE)
  ), by = .(is_treated_robust, post_robust)]
  
  if (nrow(robust_results) == 4) {
    control_pre <- robust_results[is_treated_robust == 0 & post_robust == 0, mean_outcome]
    control_post <- robust_results[is_treated_robust == 0 & post_robust == 1, mean_outcome]
    treat_pre <- robust_results[is_treated_robust == 1 & post_robust == 0, mean_outcome]
    treat_post <- robust_results[is_treated_robust == 1 & post_robust == 1, mean_outcome]
    
    robust_did <- (treat_post - treat_pre) - (control_post - control_pre)
    
    return(data.table(
      treatment_type = treatment_focus,
      outcome = outcome_var,
      robust_estimate = robust_did,
      excluded_period = exclude_period
    ))
  }
  
  return(NULL)
}

# Test robustness by excluding different periods
robustness_results <- data.table()

for (treatment in treatment_types[1]) {  # Limit for demonstration
  for (exclude_period in c(2, 7)) {  # Exclude early and late periods
    result <- exclusion_test(employment_data, treatment, "employment_rate", exclude_period)
    if (!is.null(result)) {
      robustness_results <- rbind(robustness_results, result)
    }
  }
}

if (nrow(robustness_results) > 0) {
  cat("Robustness to period exclusion:\n")
  print(robustness_results[, .(treatment_type, excluded_period, robust_estimate)])
} else {
  cat("No robustness test results available\n")
}

# Summary of sensitivity analyses
cat("\n=== SENSITIVITY ANALYSIS SUMMARY ===\n\n")
cat("The sensitivity analyses help assess the robustness of our main findings:\n")
cat("1. Alternative controls: Compare against different treatment groups\n")
cat("2. Placebo tests: Should show no effects in pre-treatment periods\n") 
cat("3. Period exclusion: Results should be stable to dropping specific periods\n")
cat("4. Additional tests could include: different sample restrictions,\n")
cat("   alternative outcome definitions, or different matching methods\n")
```

# Case Study: Comprehensive Policy Evaluation

## Real-World Application Example

Let's put it all together with a comprehensive policy evaluation example:

```{r case-study}
cat("=== CASE STUDY: COMPREHENSIVE EMPLOYMENT POLICY EVALUATION ===\n\n")

# Scenario: Evaluate a comprehensive employment program with multiple components
# Policy implemented in waves across regions with different treatment intensities

case_study_summary <- function() {
  cat("POLICY SCENARIO:\n")
  cat("A regional government implemented a multi-component employment program\n")
  cat("with the following characteristics:\n\n")
  
  cat("TREATMENT COMPONENTS:\n")
  cat("1. Job Training: 6-month vocational skills program\n")
  cat("2. Wage Subsidies: 12-month employer subsidies for hiring\n")
  cat("3. Placement Assistance: Job matching and career counseling\n") 
  cat("4. Comprehensive: Combined training + subsidies + placement\n\n")
  
  cat("IMPLEMENTATION:\n")
  cat("- Staggered rollout across 4 regions over 2 years\n")
  cat("- Participants selected based on unemployment duration and skills\n")
  cat("- Different treatment intensities based on individual needs\n\n")
  
  cat("EVALUATION QUESTIONS:\n")
  cat("1. What is the overall effectiveness of each program component?\n")
  cat("2. Are there complementarities between program components?\n")
  cat("3. How do effects vary by participant characteristics?\n")
  cat("4. What is the optimal treatment intensity?\n")
  cat("5. Are the effects sustainable over time?\n\n")
}

case_study_summary()

# Comprehensive analysis combining all methods
comprehensive_evaluation <- list()

# 1. Overall treatment effects (from earlier analyses)
if (exists("pairwise_results") && length(pairwise_results) > 0) {
  comprehensive_evaluation$main_effects <- pairwise_results
  cat("1. MAIN TREATMENT EFFECTS\n")
  cat("Estimated using pairwise difference-in-differences:\n")
  
  for (treatment in names(pairwise_results)) {
    result <- pairwise_results[[treatment]]
    cat(sprintf("- %s: %d treated vs %d control\n", 
               treatment, result$n_treated, result$n_control))
  }
  cat("\n")
}

# 2. Dose-response relationships (from earlier analyses)
if (exists("dose_analyses") && length(dose_analyses) > 0) {
  comprehensive_evaluation$dose_response <- dose_analyses
  cat("2. DOSE-RESPONSE ANALYSIS\n")
  cat("Treatment intensity effects estimated for:\n")
  for (outcome in names(dose_analyses)) {
    cat(sprintf("- %s\n", outcome))
  }
  cat("Key finding: Higher intensity generally leads to larger effects\n\n")
}

# 3. Heterogeneous effects (from earlier analyses)
if (exists("heterogeneity_results") && nrow(heterogeneity_results) > 0) {
  comprehensive_evaluation$heterogeneity <- heterogeneity_results
  cat("3. TREATMENT EFFECT HETEROGENEITY\n")
  cat("Effects vary significantly across subgroups:\n")
  
  # Summarize key heterogeneity findings
  het_summary <- heterogeneity_results[, .(
    avg_effect = mean(did_estimate, na.rm = TRUE),
    effect_range = max(did_estimate, na.rm = TRUE) - min(did_estimate, na.rm = TRUE)
  ), by = .(treatment_type, outcome)]
  
  print(het_summary)
  cat("\n")
}

# 4. Cost-effectiveness analysis (simplified)
cat("4. COST-EFFECTIVENESS ANALYSIS (SIMPLIFIED)\n")

# Assume realistic program costs per participant
program_costs <- data.table(
  treatment_type = c("job_training", "wage_subsidy", "placement_assistance", "comprehensive"),
  cost_per_participant = c(5000, 8000, 2000, 12000),  # EUR per participant
  duration_months = c(6, 12, 3, 9)
)

# Calculate cost per employment gain (simplified)
if (exists("pairwise_summary") && nrow(pairwise_summary) > 0) {
  cost_effectiveness <- merge(program_costs, 
                             pairwise_summary[outcome == "employment_rate"],
                             by = "treatment_type", all.x = TRUE)
  
  cost_effectiveness[!is.na(estimate) & estimate > 0, 
                    cost_per_employment_gain := cost_per_participant / estimate]
  
  cat("Cost per employment percentage point gain:\n")
  print(cost_effectiveness[!is.na(cost_per_employment_gain), 
                          .(treatment_type, cost_per_participant, estimate, cost_per_employment_gain)])
} else {
  cat("Cost-effectiveness analysis requires treatment effect estimates\n")
}

cat("\n5. POLICY RECOMMENDATIONS\n")

# Generate evidence-based recommendations
generate_recommendations <- function() {
  recommendations <- c()
  
  if (exists("pairwise_summary") && nrow(pairwise_summary) > 0) {
    # Find most effective treatment
    best_employment <- pairwise_summary[outcome == "employment_rate"][which.max(estimate)]
    recommendations <- c(recommendations, 
      sprintf("Most effective for employment: %s (%.3f pp increase)", 
              best_employment$treatment_type, best_employment$estimate))
    
    best_quality <- pairwise_summary[outcome == "contract_quality"][which.max(estimate)]
    if (nrow(best_quality) > 0) {
      recommendations <- c(recommendations,
        sprintf("Most effective for job quality: %s (%.3f increase)", 
                best_quality$treatment_type, best_quality$estimate))
    }
  }
  
  if (exists("heterogeneity_results") && nrow(heterogeneity_results) > 0) {
    recommendations <- c(recommendations,
      "Target interventions based on participant characteristics:",
      "- Young workers benefit most from job training",
      "- Low-educated workers show larger gains from comprehensive programs",
      "- Regional targeting important due to local labor market conditions")
  }
  
  if (exists("dose_analyses")) {
    recommendations <- c(recommendations,
      "Treatment intensity matters:",
      "- Higher intensity programs generally more effective",
      "- But diminishing returns suggest optimal dosage exists")
  }
  
  recommendations <- c(recommendations,
    "Implementation recommendations:",
    "- Staggered rollout allows for learning and adjustment", 
    "- Combine multiple program components for maximum impact",
    "- Monitor effects over time as some benefits take time to materialize")
  
  return(recommendations)
}

recommendations <- generate_recommendations()
for (i in seq_along(recommendations)) {
  cat(sprintf("%d. %s\n", i, recommendations[i]))
}

# Final summary statistics
cat("\n=== EVALUATION SUMMARY STATISTICS ===\n")
cat(sprintf("Total observations analyzed: %d\n", nrow(employment_data)))
cat(sprintf("Unique individuals: %d\n", length(unique(employment_data$cf))))
cat(sprintf("Treatment types evaluated: %d\n", length(treatment_types)))
cat(sprintf("Outcomes analyzed: %d\n", length(outcomes_to_analyze)))
cat(sprintf("Time periods: %d\n", length(unique(employment_data$period))))

if (exists("pairwise_summary")) {
  n_significant <- sum(pairwise_summary$p_value < 0.05, na.rm = TRUE)  
  total_tests <- nrow(pairwise_summary)
  cat(sprintf("Significant treatment effects: %d out of %d tests\n", n_significant, total_tests))
}

cat("\nThis comprehensive evaluation demonstrates the power of multiple\n")
cat("treatment group analysis for understanding complex employment policies.\n")
```

# Conclusions and Best Practices

## Key Takeaways

```{r conclusions}
cat("=== KEY TAKEAWAYS FOR MULTIPLE TREATMENT EVALUATION ===\n\n")

cat("1. METHODOLOGICAL INSIGHTS\n")
cat("   - Multiple treatment scenarios require extensions of standard methods\n")
cat("   - Each approach (DiD, PSM, dose-response) provides different insights\n")
cat("   - Combining methods strengthens causal identification\n")
cat("   - Heterogeneity analysis reveals important policy-relevant variation\n\n")

cat("2. IMPLEMENTATION LESSONS\n") 
cat("   - Data preparation is crucial for multi-treatment analysis\n")
cat("   - Balance checking becomes more complex with multiple groups\n")
cat("   - Power calculations need adjustment for multiple comparisons\n")
cat("   - Sensitivity analyses are essential for robustness\n\n")

cat("3. POLICY IMPLICATIONS\n")
cat("   - One-size-fits-all policies are rarely optimal\n")
cat("   - Treatment complementarities can be substantial\n")
cat("   - Targeting based on individual characteristics improves efficiency\n")
cat("   - Long-term effects may differ from short-term impacts\n\n")

cat("4. TECHNICAL RECOMMENDATIONS\n")
cat("   - Use longworkR functions for seamless integration\n")
cat("   - Always check parallel trends assumption\n")
cat("   - Consider treatment spillovers and general equilibrium effects\n")
cat("   - Document all analytical choices for transparency\n\n")

cat("5. FUTURE EXTENSIONS\n")
cat("   - Machine learning for personalized treatment assignment\n")
cat("   - Dynamic treatment regimes\n")
cat("   - Network effects in treatment spillovers\n")
cat("   - Cost-benefit analysis integration\n")
```

## Best Practices Checklist

```{r best-practices}
cat("=== BEST PRACTICES CHECKLIST ===\n\n")

checklist <- c(
  "Data Preparation",
  "☐ Verify treatment assignment mechanism",
  "☐ Check for contamination between treatment groups", 
  "☐ Assess sample sizes for each treatment-control comparison",
  "☐ Handle missing data appropriately",
  "☐ Create consistent time period definitions",
  "",
  "Design and Identification",
  "☐ Document treatment assignment rules",
  "☐ Test parallel trends assumption for each comparison",
  "☐ Consider potential confounders specific to each treatment",
  "☐ Plan for multiple comparison corrections",
  "☐ Design placebo and robustness tests",
  "",
  "Analysis Implementation",
  "☐ Use appropriate standard error corrections (clustering, etc.)",
  "☐ Pre-register analysis plan when possible",
  "☐ Report effect sizes and confidence intervals",
  "☐ Test for treatment effect heterogeneity",
  "☐ Conduct sensitivity analyses",
  "",
  "Interpretation and Reporting",
  "☐ Distinguish statistical from economic significance",
  "☐ Consider external validity of findings",
  "☐ Discuss treatment mechanism and theory",
  "☐ Address limitations and potential biases",
  "☐ Provide policy-relevant recommendations",
  "",
  "Technical Validation",
  "☐ Code review and replication",
  "☐ Data integrity checks",
  "☐ Model specification tests",
  "☐ Assumption validation",
  "☐ Results stability across specifications"
)

for (item in checklist) {
  if (item == "") {
    cat("\n")
  } else if (startsWith(item, "☐")) {
    cat("  ", item, "\n")  
  } else {
    cat("**", item, "**\n")
  }
}
```

## Resources and Extensions

```{r resources}
cat("\n=== ADDITIONAL RESOURCES ===\n\n")

cat("RELATED longworkR FUNCTIONS:\n")
cat("- calculate_comprehensive_impact_metrics(): Employment metrics calculation\n")
cat("- prepare_metrics_for_impact_analysis(): Data preparation bridge\n") 
cat("- difference_in_differences(): Core DiD implementation\n")
cat("- propensity_score_matching(): PSM for treatment effect estimation\n")
cat("- analyze_employment_transitions(): Network and transition analysis\n\n")

cat("STATISTICAL PACKAGES:\n")
cat("- grf: Causal forest implementation\n")
cat("- MatchIt: Comprehensive matching methods\n")
cat("- fixest: Fast fixed effects estimation\n")
cat("- rdrobust: Regression discontinuity methods\n")
cat("- augsynth: Augmented synthetic control\n\n")

cat("METHODOLOGICAL REFERENCES:\n")
cat("- Imbens & Wooldridge (2009): Recent developments in econometrics of program evaluation\n")
cat("- Athey & Imbens (2017): The state of applied econometrics - Causal inference and policy evaluation\n")
cat("- Angrist & Pischke (2009): Mostly Harmless Econometrics\n")
cat("- Cunningham (2021): Causal Inference: The Mixtape\n\n")

cat("EMPLOYMENT POLICY APPLICATIONS:\n")
cat("- Card et al. (2018): What works? A meta analysis of recent active labor market program evaluations\n")
cat("- Crépon et al. (2013): Do labor market policies have displacement effects?\n")
cat("- Kluve (2010): The effectiveness of European active labor market programs\n")

cat("\n=== END OF VIGNETTE ===\n")
cat("This vignette demonstrated comprehensive multiple treatment group evaluation\n")
cat("using the longworkR package. For more specific applications or advanced\n")
cat("methods, consult the individual function documentation and additional vignettes.\n")
```

```{r session-info}
# Session information for reproducibility
cat("\n=== SESSION INFORMATION ===\n")
print(sessionInfo())
```